---
title: "Processing_LiDAR_data"
author: "Ben Renne"
date: "22 November 2018"
output: html_document
---

###Setting up working environment
```{r, message=FALSE}
library(envimaR)
root_folder = alternativeEnvi(root_folder = "~/edu/mpg-envinsys-plygrnd", 
                              alt_env_id = "COMPUTERNAME",
                              alt_env_value = "PCRZP", 
                              alt_env_root_folder = "F:\\BEN\\edu")
source(file.path(root_folder, "mpg-envinfosys-teams-2018-bjcm_rs_18/src/000_setup.R"))
```

###Proceed .las files
Load files in a list
```{r}
las_files <- list.files(envrmt$path_lidar_org, pattern = glob2rx("*.las"),
                        full.names = TRUE)
```

Write .lax files for the .las files
```{r, eval=FALSE}
for (f in las_files) {
  writelax(f)
}
```

Read files (example)
```{r}
#U4745630.las as example file in the presented path
lidar_file <- readLAS(file.path(envrmt$path_lidar_org, "U4745630.las"))
plot(lidar_file, bg ="white", color = "Z")
```

###Create a catalog
Create a catalog and define its projection
```{r}
lcat <- catalog(envrmt$path_lidar_org)
lcat@crs <- CRS("+init=epsg:25832")
cores(lcat) <- 3L#how much cores of the computer are used
tiling_size(lcat) = 500#size of the subtiles 

plot(lcat)
```

###Define a catalog for the area of interest (AOI)
Read the shapefile and define a bounding box around it
```{r}
aoi <- readOGR(file.path(envrmt$path_data_mof, "AOI_mofshape.shp"))#shapefile with the AOI
aoi_bb <- bbox(aoi)#bounding box of shapefile
lasclipRectangle(lcat, xleft = aoi_bb[1], ybottom = aoi_bb[2],
                 xright = aoi_bb[3], ytop = aoi_bb[4],
                 ofile = file.path(envrmt$path_tmp, "las_mof_aoi.las"))#write .las file
```

Create a.lax file for the AOI-LAS file and create a catalog for this area
```{r}
writelax(file.path(envrmt$path_tmp, "las_mof_aoi.las"))
lcat <- catalog(file.path(envrmt$path_tmp, "las_mof_aoi.las"))
lcat@crs <- CRS("+init=epsg:25832")
cores(lcat) <- 3L
tiling_size(lcat) = 500
buffer(lcat) = 0#Output = one tile for the whole MOF
```

Retile the AOI.las into 500m parts
```{r}
lcat_tiled <- catalog_retile(lcat, envrmt$path_clip, "las_mof_aoi_")
lcat_tiled@crs <- CRS("+init=epsg:25832")
cores(lcat_tiled) = 3L
tiling_size(lcat_tiled) = 500
buffer(lcat_tiled) = 0#Output = retiled tile

plot(lcat_tiled)
```

###Surface model
Compute surface model with 0.5 m resolution and convert it to a raster object.
```{r}
lchm = grid_canopy(lcat_tiled, 0.5, subcircle = 0.2)
lchmr = as.raster(lchm)
crs(lchmr) = lcat@crs

mapshot(mapview(lchmr), url = file.path(envrmt$path_clip, "lidar_dhm_map.html"))#.html file is written to the output location
```

