---
title: "Processing optical data"
author: "Ben Renne"
date: "16 November 2018"
output: html_document
---

###Set working environment
```{r working environment, message=FALSE}
library(envimaR)
root_folder = alternativeEnvi(root_folder = "~/edu/mpg-envinsys-plygrnd", 
                              alt_env_id = "COMPUTERNAME",
                              alt_env_value = "PCRZP", 
                              alt_env_root_folder = "F:\\BEN\\edu")
source(path.expand("~/edu/mpg-envinsys-plygrnd/mpg-envinfosys-teams-2018-bjcm_rs_18/src/000_setup.R"))
```

###Load links to images
```{r}
list_files <- list.files(paste0(envrmt$path_aerial_org), pattern = ".tif")
list_files
```

###Load links to images in memory
```{r}
imagelist <- list()
for (i in list_files) {
  imagelist[[i]] <- brick(file.path(envrmt$path_aerial_org, i))
}
```

###Rename files in list to assign every image to its position
- position number is pasted in front of the file name
```{r}
for (j in seq(1:length(imagelist))) {
  names(imagelist)[j] <- paste(j, list_files[j], sep = "_") 
}
```

###Identify rojections
```{r}
projct <- c()#create an empty vector
for (x in imagelist) {
  v <- crs(x)#identify coordinate system
  projct <- c(projct, v)
}
projct
```

###Load shapefile and check the coordinate system
```{r}
shape1 <- readOGR(file.path(envrmt$path_data_mof, "AOI_mofshape.shp"),
                  layer = ogrListLayers(file.path(envrmt$path_data_mof, "AOI_mofshape.shp")))#normally "wcAbteilung.shp" should be loaded, but just a few "Abteilungen" are interested for the research question
#should be automated with a loop

crs(shape1)#check coordinate system of the shapefile
```

###Crop images on the extent of AOI
```{r, eval=FALSE}
cropped <- lapply(imagelist[3:length(imagelist)], crop, shape1)
```

###Mosaic overlapping images
```{r, eval=FALSE}
imagelist3_4 <- mosaic(cropped$`3_476000_5630000.tif`, cropped$`4_476000_5630000_1.tif`, fun="min",overwrite=FALSE, filename=paste0(envrmt$path_data_aerial_processe, "image3_4.tif"))

imagelist5_6 <- mosaic(cropped$`5_476000_5632000.tif`, cropped$`6_476000_5632000_1.tif`, fun="min",overwrite=FALSE, filename=paste0(envrmt$path_data_aerial_processe, "image5_6.tif"))
```

###Merging of the images
```{r, eval=FALSE}
aoiimg <- merge(imagelist3_4, imagelist5_6, cropped$`7_478000_5630000.tif`, cropped$`8_478000_5632000.tif`, overwrite=FALSE, filename=paste0(envrmt$path_data_aerial_processe, "AOIimage.tif"))
```

###Plot the images and the cropped shape
```{r}
plotRGB(brick(file.path(envrmt$path_processed, "AOIimage.tif")))
plot(shape1, add=TRUE, col = alpha("blue", alpha = 0.3))
```
